---
title: "NewFile"
author: "Jenit Jain"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Types

Data structures are very important to understand because these are the objects you will manipulate on a day-to-day basis in R. Dealing with object conversions is one of the most common sources of frustration for beginners. Everything in R is an object.

R has 5 basic data types.

- character
- numeric (real or decimal)
- integer
- logical
- complex

```{r}
i <- 1L
b <- TRUE

paste0(i, " is of type ", class(i))
paste0(b, " is of type ", class(b))
```

## Lists and Vectors

A vector is a one dimensional array of elements. Vectors are the basic building blocks of R. Almost all data in R is stored in a vector, or even a vector of vectors.

Lists are one of the most flexible data structures in R. As a result, they are used as a general purpose glue to hold objects together. You will find lists disguised as model objects, data frames, list-columns within data frames, and more. A list is a recursive vector: a vector that can contain another vector or list in each of its elements.

```{r}
list1 <- list(1, "Jenit", "MDS", TRUE)
vec1 <- c(1, 2, 3, 4, "Jenit")
```

```{r}
print("The list is: ")
list1
```
```{r}
print("The vector is: ")
vec1
```

A list can contain elements of different datatype where a vector coerces the data types of its elements so that all the elements in the vector have the same data type 
